\thesistitle

### 2019-07-19 sections/conclusion.tex
More about stuff

\subsection{Refactoring the harder to refactor clones}

@@

In a recent study by Alon et al. \cite{alon2018code2seq} they propose code2seq. Code2seq is a machine learning model that guesses the name of a method given a method body. This model has been trained on a large set of method bodies and names. The model already shows promising results. The source code of code2seq is publicly available, making it possible to embed this model in any application. Although this model is still far from perfect, combining it with our research could already greatly reduce the manual refactoring effort required. The main deficiency of this model lies in that its limited to the directly avail

>>>>

\subsection{Refactoring the harder to refactor clones}
In section \ref{sec:refactorability} we introduced to what extent clones can be refactored through method extraction. Because we strived to get results fast, we excluded catagories that could not not be directly refactored through method extraction. However, with a few transformations or further considerations it might be possible to make these clones refactorable.

@@

In a recent study by Alon et al. \cite{alon2018code2seq} they propose code2seq. Code2seq is a machine learning model that guesses the name of a method given a method body. This model has been trained on a large set of method bodies and names. The model already shows promising results. The source code of code2seq is publicly available, making it possible to embed this model in any application. Although this model is still far from perfect, combining it with our research could already greatly reduce the manual refactoring effort required. The main deficiency of this model lies in that its limited to the method body and does currently not consider anything else in a method body. This method is flawed, because the meaning of method bodies depends heavily on their context. For instance, the body of the method \texttt{get()} in \texttt{ArrayList} does not make any sense in relation to its name without considering its context (class, inheritance hierarchy, etc.).
